---
title: "Covid91 vaccine study Final2022"
author: "Juan Moreno"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`" 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
FinalDat <-read.csv(file="final_Data.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalDat  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
options(digits = 1)
```

# Introduction


A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

```{r, include='FALSE'}
# Not included to make things look neater  
Males<- filter(FinalData, sex== "M"); 
Females <- filter(FinalData, sex== "F")
lgbtq <- filter(FinalData, LGBTQ=="gay")
druggies <- filter(FinalData, DrugUser=="yes")
```


## Males


### Descriptive Results


#### Graphical Descriptive Results

```{r}
ddm <- Males %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicCm <- ggplot(ddm,aes(x=infected,y=count,fill= treatment))
basicCm + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCCm <- ggplot(ddm,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCCm + geom_bar(stat="identity", position = "dodge")
```

After creating a group made up of purely males we take   the data and create a bar chart so there can be a   visual of he data of the vaccine effectiveness when   used on males.    



#### Numerical Descriptive Results


```{r}
table1m <- xtabs(~infected + treatment, data=Males)
rowPerc(table1m)
colPerc(table1m)
```

Taking the group purely made of males once more, we now   have created a data sheet, that show the same as the   visual above, showing that the vaccine is working for   males.  

### Inferential Results

```{r}
chisq.test(table1m)
chisqtestGC(table1m)
malefisher<- fisher.test(table1m)
malefisher
```

Here we have taken the male group for one last time and     have ran the Fisher's Exact test. This shows that the     p-value proves that those who have taken the placebo     are more likely to catch Covid.    

### Efficacy

```{r}
#used to create efficacy for males


efficacym <- ((malefisher$estimate/(1+malefisher$estimate)*100))

malefisherlow <- (malefisher$conf.int[1])

malefisherhigh<- (malefisher$conf.int[2])

efficacymalelow <- (malefisherlow/(1+malefisherlow)*100)

efficacymalehigh <- (malefisherhigh/(1+malefisherhigh)*100)
```


With the efficacy being `r efficacym`% Here we have the confidence interval of 95%  from `r efficacymalelow` to `r efficacymalehigh`. 


### Conclusion and Recommendation



Looking at all the evidence I can confidently say that for males as a group they should take the vaccine as it lowers the chances of   catching covid. As we were looking at the information we can also say that there was little to no mistake as supported by Fisher's exact test.  



## Females

### Descriptive Results

#### Graphical Descriptive Results

```{r}
ddf <- Females %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicCf <- ggplot(ddf,aes(x=infected,y=count,fill= treatment))
basicCf + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCCf <- ggplot(ddf,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCCf + geom_bar(stat="identity", position = "dodge")
```


Looking at the graph we can see that in numbers both placebo and    vaccine that were given out seems to be equal. Looking at the   percentage graph we can see that those who have given the placebo   contracted covid then those who taken the vaccine.  


#### Numerical Descriptive Results

```{r}
table1f <- xtabs(~infected + treatment, data=Females)
rowPerc(table1f)
colPerc(table1f)
```

Looking at the numerical results for the graph above we can see that   even numerical wise we see that again those who have taken the   vaccine we can see that they are less likely to contract covid.   


### Inferential Results

```{r}
chisq.test(table1f)
chisqtestGC(table1f)
fisher.test(table1f)
femalefisher<- fisher.test(table1f)
femalefisher
```

Taking the data and running the data through Fisher's exact test, we can see that the p-value proves that taking the vaccine can be   helpful then not taking it.  



### Efficacy 

```{r}
#used to create efficacy for males


efficacyf <- ((femalefisher$estimate/(1+femalefisher$estimate)*100))

femalefisherlow <- (femalefisher$conf.int[1])

femalefisherhigh<- (femalefisher$conf.int[2])

efficacyfemalelow <- (femalefisherlow/(1+femalefisherlow)*100)

efficacyfemalehigh <- (femalefisherhigh/(1+femalefisherhigh)*100)
```


With the efficacy being `r efficacyf`% Here we have the confidence interval of 95%  from `r efficacyfemalelow` to `r efficacyfemalehigh`. 




### Conclusion and Recommendation

At a glace we can see that it's hard to tell but using fisher's exact test and looking at the confidence interval results, in   conclusion its best for females to take the vaccine as it has a slighter chance of not catching covid.  





## LGBTQ


### Descriptive Results

#### Graphical Descriptive Results

```{r}
ddQ <- lgbtq %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicCQ <- ggplot(ddQ,aes(x=infected,y=count,fill= treatment))
basicCQ + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCCQ <- ggplot(ddQ,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCCQ + geom_bar(stat="identity", position = "dodge")
```


Taking a look at the LGBTQ community we can see that those who have taken the vaccine contracted covid then those who have taken the placebo. This is also true when looking at the percentage graph.  


#### Numerical Descriptive Results

```{r}
table1Q <- xtabs(~infected + treatment, data=lgbtq)
rowPerc(table1Q)
colPerc(table1Q)
```

Taken the data and putting it into numerical terms we can see specific numeber as well as percentage of the data.  

### Inferential Results

```{r}
chisq.test(table1Q)
chisqtestGC(table1Q)
fisher.test(table1Q)
Qfisher<- fisher.test(table1Q)
Qfisher
```

As we look at the Fisher's Exact test we see that the p-value does lead us to believe that there is a difference but taking what is   known we see that those who have taken the placebo will do better then those who take the vaccine.  

### Efficacy 


```{r}
#used to create efficacy for males


efficacyQ <- ((Qfisher$estimate/(1+Qfisher$estimate)*100))

Qfisherlow <- (Qfisher$conf.int[1])

Qfisherhigh<- (Qfisher$conf.int[2])

efficacyQlow <- (Qfisherlow/(1+Qfisherlow)*100)

efficacyQhigh <- (Qfisherhigh/(1+Qfisherhigh)*100)
```


With the efficacy being `r efficacyQ`% Here we have the confidence interval of 95%  from `r efficacyQlow` to `r efficacyQhigh`.   


### Conclusion and Recommendation

Surprisingly when looking at all the data we can see that the LGBTQ community should not take the vaccine as it will make them most likely to contract covid, then those who have taken the placebo.



## Druggies





### Descriptive Results

#### Graphical Descriptive Results

```{r}
ddd <- druggies %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicCd <- ggplot(ddd,aes(x=infected,y=count,fill= treatment))
basicCd + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCCd <- ggplot(ddm,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCCd + geom_bar(stat="identity", position = "dodge")
```

Looking at the graph we can clearly see that those who have taken the vaccine are more likely to catch covid, and this carries out when   we look at the graph percentage wise.  




#### Numerical Descriptive Results

```{r}
table1d <- xtabs(~infected + treatment, data=druggies)
rowPerc(table1d)
colPerc(table1d)
```

Looking at the numerical results we can see specific numbers and percentage of how many are infected in the group.  


### Inferential Results

```{r}
chisq.test(table1d)
chisqtestGC(table1d)
fisher.test(table1d)
dfisher<- fisher.test(table1d)
dfisher
```
As we take a look at the Fisher's exaxt test, the P-value supoorts our idea of the vaccine not working on druggies.  

### Efficacy 


```{r}
#used to create efficacy for males


efficacyd <- ((dfisher$estimate/(1+dfisher$estimate)*100))

dfisherlow <- (dfisher$conf.int[1])

dfisherhigh<- (dfisher$conf.int[2])

efficacydlow <- (dfisherlow/(1+dfisherlow)*100)

efficacydhigh <- (dfisherhigh/(1+dfisherhigh)*100)
```


With the efficacy being `r efficacyd`% Here we have the confidence interval of 95%  from `r efficacydlow` to `r efficacydhigh`.    



### Conclusion and Recommendation

Without a surprise people who do drugs should not take the vaccine as it increases the chances of contracting covid greatly, then if   they were to not take the vaccine. I believe this is due to drug use as it can weaken the system and making other vaccines or drugs   useless.  


